MONID

### 2023-09-12 Presentation/presentation.tex
update

\begin{frame}
    \frametitle{Conclusions}

>>>>

\begin{frame}
    \frametitle{Conclusions}
    In conclusion:
    \begin{itemize}
        \item We have introduced the MONID framework and explained how it works.
        \item We then proceeded introducing a new temporal logic named EAGLE, which serves as the foundation for the MONID framework.
        \item We have presented some example of formulas which aims at recognize some attacks patterns.
    \end{itemize}
    \vspace{2.5mm}
    Due to the little overhead involved in the computation and the great performances of MONID when utilized offline, we can state that this method should still be useful in theory today.
\end{frame}
